---
title: "Homework 6"
author: "Rachel Tsong"
date: "27 November 2018"
output: github_document
---

```{r}
library(tidyverse)
library(modelr)
```

# Problem 1
```{r }
## Import and clean data by creating binary variables for unsolved dispositions and race, filter out irrelevant cities
homicide = read_csv(url("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")) 

homicide = homicide %>%
  mutate(city_state = str_c(city, state, sep = ", "),
         resolved = as.numeric(disposition == "Closed by arrest"),
         victim_age = as.numeric(victim_age),
         victim_race = ifelse(victim_race == "White", c("White"), c("Non-white")),
         victim_race = fct_relevel(victim_race, "White")) %>%
  filter(city_state != "Dallas, TX" & 
         city_state != "Phoenix, AZ" & 
         city_state != "Kansas City, MO" & 
         city_state != "Tulsa, AL")
```

In the code chunk above, I imported and cleaned the data. At first I was worried about the warning message when I recoded `victim_age` as a factor variable, but upon looking at the original data set there were instances in which the victim's age was unknown. These were changed to NAs when recoded to numeric, so I didn't see this as a problem.

```{r}
## Fit logistic regression using age, race, and sex as predictors for resolved
baltimore_logistic = 
  homicide %>% 
  filter(city_state== "Baltimore, MD") %>%
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) 

## Make a table showing the odds ratio and 95% CI 
baltimore_logistic %>%  
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
         OR_upper_bound = exp(estimate + 1.96*std.error),
         OR_lower_bound = exp(estimate - 1.96*std.error)) %>%
  select(term, starts_with("OR")) %>%
  filter(term == "victim_raceNon-white") %>%
  knitr::kable(digits = 3)
```

From this regression model, the odds of a homicide of a non-white victim being resolved in Baltimore is 0.44 times the odds of a homicide of a white victim being resolved, holding all other variables constant. We are 95% confident that the true odds ratio is between 0.31 and 0.62.

```{r}
## Apply logistic regression function to each city, save results as a dataframe showing ORs and 95% CIs
homicide_logistic = homicide %>%
  group_by(city_state) %>%
  nest() %>%  
  mutate(regression = map(data, ~glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial())),
         regression = map(regression, broom::tidy)) %>% 
  select(-data) %>%
  unnest()%>% 
  mutate(OR = exp(estimate),
         OR_upper_bound = exp(estimate + 1.96*std.error),
         OR_lower_bound = exp(estimate - 1.96*std.error)) %>%
  select(city_state, term, starts_with("OR")) %>%
  filter(term == "victim_raceNon-white") 
```

```{r}
## Make a plot show ORs and CIs from each city
homicide_logistic %>%
  mutate(city_state = fct_reorder(city_state, OR)) %>%
  ggplot(aes(x = city_state, y = OR)) +
    geom_point() +
    coord_flip() +
    geom_errorbar(aes(ymin = OR_lower_bound, ymax = OR_upper_bound)) +
    labs(x = "Location", y = "Odds Ratio", title = "Odds Ratios of Non-white Homicides being Resolved Compared to White Homicides") +
    geom_hline(yintercept = 1, color = "red") +
    theme_bw() 
```

From this plot, we can see that in most large US cities, the odds ratio of a non-white homicide being resolved compared to a white homicide being resolved is less than 1.0, indicating that less non-white homicides are solved (holding all other variables constant). However, there are several cities where the 95% CI includes 1.0, so further investigation into these cities is required in order to determine if the true OR is less than 1.0. 


## Problem 2
```{r}
birthweight = read_csv("./birthweight.csv") %>%
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace),
         mrace = as.factor(mrace),
         malform = as.factor(malform)) 
```

```{r}
bw_model_1 = lm(bwt ~ blength + ppbmi + smoken, data = birthweight)
```

My model for predicting an infants birthweight includes 3 predictors. First, I chose the baby's length at birth. Although height is not a completely accurate predictor for a human height due to differing BMIs, I still think that a baby's length is pretty well correlated to birthweight. I also added the mother's pre-pregnancy BMI. Obviously the mother and child share DNA, so the mother's body type could be correlated to the child's body type. I chose BMI over other factors such as height and weight because BMI incorporates both of these variables. Lastly, I chose number of cigarettes smoked per day during pregnancy because if there's anything Mailman has taught me, it's that smoking is bad! I predict that birthweight is negatively correlated with number of cigarette's smoked. For my model, I decided that 3 predictors would be enough to ensure parsimony.

```{r}
birthweight %>%
  add_predictions(., bw_model_1) %>%
  add_residuals(., bw_model_1) %>%
  ggplot(aes(x = pred, y = resid)) + 
    geom_point() +
    geom_hline(yintercept = 0, color = "red") +
    labs(x = "Fitted Values", y = "Residuals", title = "Residual vs Fit Plot for My Model") +
    theme_bw()
```




